Spatial Reasoning and Statistical Graphics

### 2014-10-11 Paper/Draft1/TestingVisualAptitude.Rnw
additional comments

\comment{We might need to expand this a bit to account for the figure classification section, which has some questions with 2 answers and some with 3. Or we could leave it as an exercise for the reader :)}

>>>>

\comment{\textit{We might need to expand this a bit to account for the figure classification section, which has some questions with 2 answers and some with 3. Or we could leave it as an exercise for the reader :)}}

\comment{\textit{So are we scaling things by the variance/std dev. under random guessing? Or by the theoretical test range?}}
